Improvement of crash forces in structures using optimization tools.

### 2016-07-27 paper.tex
Avances

On the other hand, structural adhesives have improved their mechanical properties in recent years and can be now used with confidence in heavy duty applications. Interest on them is also raising up in scientific fields thanks to these enhancements and to the recent development of validated numerical models.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{./figures/IMG_CUTRES/comparison}
	\caption[Qualitative strength and cost comparison of different joining solutions.]{Qualitative strength and cost comparison of different joining solutions. Taken from \cite{superyacht}.}
	\label{fig:comparison}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{figures/IMG_CUTRES/medidas_cb}
	\caption{Dimensions of the modeled crash boxes, in millimeters. Taken from \cite{Peroni2009}.}
	\label{fig:crash_box}
\end{figure}

@@

Before making any calculations with the force-displacement curve, and according to the specialized literature in crash analysis \citep{Huanglibro}, a standard SAE 600 filter \cite{J211} is applied. This removes the high-frequency noise from the curve with a cutoff frequency of ${1000}$ Hz. Once the filter is used, the direct integration of the resulting force-displacement curve yields to the $E_a$:
\begin{equation}\label{Ea}
  E_{a}=\int _{0}^{\delta }F\! \left( z \right) \,dz\,,
\end{equation}
with $\delta$ being the total axial crushing distance and $F\! \left( z \right)$ the value of the crushing force at the crushing length $z$.

>>>>

On the other hand, structural adhesives have improved their mechanical properties in recent years and can be now used with confidence in heavy duty applications. Interest on them is also raising up in scientific fields thanks to these enhancements and to the recent development of validated numerical models.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=\linewidth]{./figures/IMG_CUTRES/comparison}
	\caption[Qualitative strength and cost comparison of different joining solutions.]{Qualitative strength and cost comparison of different joining solutions. Taken from \cite{superyacht}.}
	\label{fig:comparison}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.6\linewidth]{figures/IMG_CUTRES/medidas_cb}
	\caption{Dimensions of the modeled crash boxes, in millimeters. Taken from \cite{Peroni2009}.}
	\label{fig:crash_box}
\end{figure}

@@

Before making any calculations with the force-displacement curve, and according to the specialized literature in crash analysis \cite{Huanglibro}, a standard SAE 600 filter \cite{J211} is applied. This removes the high-frequency noise from the curve with a cutoff frequency of ${1000}$ Hz. Once the filter is used, the direct integration of the resulting force-displacement curve yields to the $E_a$:
\begin{equation}\label{Ea}
  E_{a}=\int _{0}^{\delta }F\! \left( z \right) \,dz\,,
\end{equation}
with $\delta$ being the total axial crushing distance and $F\! \left( z \right)$ the value of the crushing force at the crushing length $z$.
